### 2020-10-19 SujetStage/2020-pNetsubjectM2.tex
skype 2

After this preliminary step, the next objective will be to design a refinement theory for open automata. We will make sure that this relation is specified in a constructive manner, so that an algorithm could be derived from the specification in the future.
The relationship between refinement and automata composition should also play a major role in this definition.

@@

The next steps in the internship will rely on these two initial works; they will consist in addressing some of the following (independent) objectives:
\begin{itemize}
\item Express and prove compositionality properties for refinement relation over open automata.
\item Study formally the behaviour of CCS operators wrt refinement.
\item Study the classification of the refinement semantics in the van Glabbeek spectrum could also be studied.
\item Design the algorithm that checks refinement between wo open automata.
\end{itemize}

>>>>

After this preliminary step, the next objective will be to design a refinement theory for open automata. We will make sure that this relation is specified in a constructive manner, so that an algorithm could be derived from the specification in the future~\cite{Bellegarde:MEMOCODE2003}.
The relationship between refinement and automata composition should also play a major role in this definition.

@@

The next steps in the internship will rely on these two initial works; they will consist in addressing some of the following (independent) objectives:
\begin{itemize}
\item Express and prove compositionality properties for refinement relation over open automata.
\item Study formally the behaviour of CCS operators wrt refinement.
\item Compare this theory with the state of the art and classify the refinement semantics in the van Glabbeek spectrum.
\item Design the algorithm that checks refinement between two open automata.
\end{itemize}
